Higher-Order unification for free!

### 2024-07-25 paper/paper_for_taps/source/main.tex
rm sty files : content moved into main.tex

\usepackage{myTools}
\usepackage{macros}
\usepackage{enumitem}
\usepackage{intcalc}
\usepackage{nameref}

@@

\usepackage{pb_printer}

>>>>

\usepackage[newfloat]{minted}
\usepackage{xspace}
\usepackage{cleveref}
\usepackage{calc}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage{intcalc}
\usepackage{nameref}

\newcommand{\hoareTriple}[3]{
  \{#1\}\ #2\ \{#3\}
}

\newcommand\sepimp{\mathrel{-\mkern-6mu*}}

\newcommand*{\eqdef}{\ensuremath{\mathrel{\overset{\mathrm{def}}{=}}}}

\def\prop{\texttt{Prop}}

% Guillemots for maths
\def\gl{\text{``}}
\def\gr{\text{''}}
\newcommand{\guillemot}[1]{\gl #1 \gr}

% after usepackage{minted}
\newcommand{\elpiIn}[1]{\mintinline[fontsize=\small,escapeinside=~~]{elpi.py:ElpiLexer -x}{#1}}
\newcommand{\elpiInFN}[1]{\mintinline[fontsize=\footnotesize,escapeinside=~~]{elpi.py:ElpiLexer -x}{#1}}
\newcommand{\coqIn}[1]{\mintinline[fontsize=\small,escapeinside=~~]{coq}{#1}}
\newcommand{\textIn}[1]{\mintinline[escapeinside=~~]{text}{#1}}

\newcommand{\elpiInEq}[2][]{
  \begin{equation}
    \texttt{\elpiIn{#2}}
    \label{#1}
  \end{equation}
}

\newcommand{\elpiInEqq}[2][]{
  \begin{equation*}
    \texttt{\elpiIn{#2}}
    \label{#1}
  \end{equation*}
}

\newcommand{\coqInEq}[2][]{
  \begin{equation}
    \texttt{\coqIn{#2}}
    \label{#1}
  \end{equation}
}

% \newminted{coq}{escapeinside=||}
% \newminted{elpi}{escapeinside=||}

\newcommand{\inputrawelpicode}[1]{%
\inputminted[fontsize=\small,autogobble,escapeinside=~~,mathescape=true,frame=leftline,framerule=0pt,framesep=0em]{elpi.py:ElpiLexer -x}{#1_raw.tex}%
}

\newenvironment{elpicode}{%
  \vspace{0.2em}%
  \VerbatimEnvironment
    \begin{minted}[fontsize=\small,autogobble,escapeinside=~~,mathescape=true,frame=leftline,framerule=0pt,framesep=1em]{elpi.py:ElpiLexer -x}%
}{%
  \end{minted}%
  \vspace{0.2em}%
}
\newenvironment{elpicodetab}{%
  \VerbatimEnvironment
    \begin{minted}[fontsize=\small,autogobble,escapeinside=~~,mathescape=true,frame=leftline,framerule=0pt,framesep=0em]{elpi.py:ElpiLexer -x}%
}{%
  \end{minted}%
  \vspace{0.2em}%
}

\newenvironment{textcode}{%
  \vspace{0.2em}%
  \VerbatimEnvironment
  \begin{minted}[breaklines,fontsize=\small,autogobble,escapeinside=~~,mathescape=true,frame=leftline,framerule=0pt,framesep=1em]{text}%
}{%
  \end{minted}%
  \vspace{0.2em}%
}

\newenvironment{coqcode}{%
  \vspace{0.2em}%
  \VerbatimEnvironment
    \begin{minted}[fontsize=\small,autogobble,escapeinside=~~,mathescape=true,frame=leftline,framerule=0pt,framesep=1em]{coq}%
}{%
  \end{minted}%
  \vspace{0.2em}%
}

% from amsmath and pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\newcommand{\proglang}[1]{\texttt{#1}\xspace}
\newcommand{\pl}[1]{\proglang{#1}}

\def\old{\noindent\hrulefill OLD \noindent\hrulefill}

\makeatletter
\newcommand{\customlabel}[2]{%
   \protected@write \@auxout {}{\string \newlabel {#1}{{\ensuremath{#2}}{\thepage}{#2}{#1}{}} }%
   \hypertarget{#1}{\ensuremath{#2}}
}
\makeatother

\newcounter{llength}
\newcommand{\listlength}[1]{
  \setcounter{llength}{0}%
  \foreach \i in #1 {\stepcounter{llength}}%
}

\newcommand*{\fullref}[1]{\cref{#1} (\textsc{\nameref{#1}})}
\newcommand*{\Fullref}[1]{\Cref{#1} (\textsc{\nameref{#1}})}

\makeatletter
\newcommand{\addXdef}[2]{\protected@xdef#1{#1 #2}}

\newcommand{\nth}[3]{
  \foreach \x [count=\k] in #2 {\ifnum\k=#3 \addXdef{#1}{\x} \fi}
}

% takes a unif symbol (\Ue or \Uo) and a list of pairs: (lhs, rhs) of unif pb
\newcommand{\printPb}[2]{
  \listlength{#2}
  \def\tableData{}% empty table
  \foreach \x [count=\i] in #2
    {
      \foreach \y [count=\j] in \x {
        \ifthenelse{\isodd{\j}}
          {\addXdef{\tableData}{\y & #1 &}}
          {\addXdef{\tableData}{\y}}
      } 
      \ifthenelse{\equal{\i}{2}}{}{
        \ifthenelse{\equal{\i}{\thellength}}{}{\addXdef{\tableData}{&\quad}}
      }
    }
  \tableData
}

% Takes a list of triple: coq-var, elpi-var, arity
\newcommand{\printMap}[1]{
  \def\tableData{}% empty table

  \newcommand{\printMapAux}[1]{
    \nth{\tableData}{##1}{1} \addXdef{\tableData}{\mapsto} 
    \nth{\tableData}{##1}{2} \addXdef{\tableData}{^} \nth{\tableData}{##1}{3}}

  \listlength{#1}
  \foreach \x [count=\i] in #1
    {
      \printMapAux{\x}
      \ifthenelse{\equal{\thellength}{\i}}{}{
        \ifthenelse{\equal{\intcalcMod{\i}{3}}{0}}
        {\addXdef{\tableData}{\\}}
        {\addXdef{\tableData}{&\quad}}
        }
    }
  \ensuremath{
    \begin{array}{ccc}
      \tableData
    \end{array}
  }
}

% Take a list of triple for eta-links: (link-type, ctx, lhs, rhs), link-type is \eta or \beta
\newcommand{\printLink}[1]{
  \listlength{#1}
  \def\tableData{}% empty table

  \newcommand{\printLinkAux}[1]{
    \nth{\tableData}{##1}{2} \addXdef{\tableData}{\vdash&} 
    \nth{\tableData}{##1}{3} \addXdef{\tableData}{&=_}
    \nth{\tableData}{##1}{1} \addXdef{\tableData}{&} 
    \nth{\tableData}{##1}{4}
  }

  \foreach \x [count=\i] in #1
    {
      \printLinkAux{\x}
      \ifthenelse{\equal{\thellength}{\i}}{}{
        \ifthenelse{\isodd{\i}}
          {\addXdef{\tableData}{&\quad}}
          {\addXdef{\tableData}{\\}}
      }
    }
  \ensuremath{
    \begin{array}{rcclrccl}
      \tableData
    \end{array}
  }
}

\newcommand{\putBigPar}[2]{
  \listlength{#1}
  \ifthenelse{\thellength>#2}{\Big}{}
}

\newcommand{\hideEmpty}[2]{
  \ifthenelse{\equal{#1}{{}}}{}{#2}
}

% Input is: 
%   P = a list of pairs for FoUnifPb    (leftPb, rightPb)
%   T = a list of pairs for HoUnifPb    (leftPb, rightPb)
%   M = a list of triples for mappings  (FoVar, HoVar, Arity)
%   L = a list of 4-uplet for links     (link-type, ctx, lhs, rhs)
% T, M, L can be empty
% Note: this macro is used when the length of P > 1
\newcommand{\printAlll}[4]{
  \arraycolsep=2pt
  $$
  \begin{array}{rrclrcll}
    \foUnifPb = \{ & \printPb{\Uo}{#1} &\}
    \hideEmpty{#2}{\\
      \hoUnifPb = \{ & \printPb{\Ue}{#2} &\}
    }
    \hideEmpty{#3}{\\
      \mapStore = \putBigPar{#3}{3}\{ & \multicolumn{7}{l}{
        \printMap{#3} ~\putBigPar{#3}{3}\}
    }}
    \hideEmpty{#4}{\\
      \linkStore = \putBigPar{#4}{2}\{ & \multicolumn{7}{l}{
        \printLink{#4} ~\putBigPar{#4}{2}\}
    }}
  \end{array}
  $$
}

% Same as printAlll, but the length of P is 1, the if then else
% seems not to work on the fst parameter of multicolumn
\newcommand{\printAlllSingle}[4]{
  \arraycolsep=2pt
  $$
  \begin{array}{rrcll}
    \foUnifPb = \{ & \printPb{\Uo}{#1} &\}
    \hideEmpty{#2}{\\
      \hoUnifPb = \{ & \printPb{\Ue}{#2} &\}
    }
    \hideEmpty{#3}{\\
      \mapStore = \putBigPar{#3}{3}\{ & \multicolumn{4}{l}{
        \printMap{#3} ~\putBigPar{#3}{3}\}
    }}
    \hideEmpty{#4}{\\
      \linkStore = \putBigPar{#4}{2}\{ & \multicolumn{4}{l}{
        \printLink{#4} ~\putBigPar{#4}{2}\}
    }}
  \end{array}
  $$
}
\makeatother

@@
